\documentclass{article}
\title{OpenDcd: An Open Source Finite State Decoding Toolkit}
\author{Paul R. Dixon}
\begin{document}

\end{document}

## Idea Stream
What does the compact representation do for a traditional decoder?

##Abstract
In this paper we introduce a very small and portable Weighted Finite State Transducer based decoding toolkit.

We provide a command line application, we believe this is the first publically avaliable toolkit that is compatible with all the major speech recognition toolkits.

and a library suitable for integration with applications such dialog systems or machine translation. We have made sample application avalaible in verious languages.

It is based on array of excellent open source software including
Sphinx,OpenFst,Juicer,Kaldi we bring our experience  and should provide the
researchers, application developers and students. We have also includes
additional tools
Although small and extremely portable, the library supports an impressive set
of state of the art features, these include WFSTs, dynamic composition and deep
nueral network acoustic model.s

In addition we make baseline pre-built models in English freely available.

##Introduction

Pioneering work was performed as AT&T where they released FSM toolkit, GRM toolkit and DCD toolkit. Recenlty, there has been open source WFST toolkit and language modelling toolkit. However, no one has provided a powerful  and easy to use decoding toolkit that can function as both a research toolkit. In this paper we describe out OpenDcd libary that solves both these problems and bring a large amount of features that will be useful to the speech and developer community at large.

##Decoding Command

##Build Command

##Post processing command

##No dependenices 

Our only dependency is OpenFst, however we bundle a version to help users (in particular those from China or using Windows or both).

Kaldi supports many state-of-the-art features and

For backwards compatability and re-use of existing models we provide converters
for Sphinx and HTK based models.

Finally, nearly all the code runs on Linux,OSX, Android, and Windows. The only
acception are a few Kaldi converions tools. However, these would be of use to
users with a full Kaldi training setup anyway.

We remove the need for the expensive static compilation and this will allow
users to experiment with new language models and grammers.


It seems that label pushing and online minimization really help the lookahead
composer.


  - We provide all dependencies and simple build systems. No need to download
  - No autotools or similarly terrbile build systems.
  - No need for a full HTK, Sphinx or Kaldi install.

  - Support Windows even the free tools
  -  No need for configure
  - Allow users to mix HTK, Kaldi and Sphinx

## Baseline Models and Experiments

Caching the destination search states really helps!

## Summary 
The code is currently avaliable as an open source project. In future versions we
would like add more free models in various language and encourage users to
contribute models and data.
It is hoped that the baseline models and decoder can be used when researchers
benchmark their own propriety decoders and techniqes to fully ascertain the


> Written with [StackEdit](https://stackedit.io/).end{document}
